\documentclass[letterpaper,11pt]{article}

\usepackage{hyperref}
\usepackage{geometry}


\usepackage[T1]{fontenc}
\usepackage[sc]{mathpazo}

\usepackage{fontawesome}

\def\name{Ali Afroozeh}


\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

\setlength\parindent{0em}

\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

{\huge \name}


\vspace{0.25in}

\faGlobe~\href{http://afroozeh.github.io/}{http://afroozeh.github.io}
\vspace{0.02in}

\faEnvelopeO~\href{mailto:afroozeh@gmail.com}{afroozeh@gmail.com}
\vspace{0.02in}

\faTwitter~\href{https://twitter.com/afruze}{afruze}
\vspace{0.02in}

\faGithub~\href{https://github.com/afroozeh}{afroozeh}

\section*{Education}

\begin{itemize}
  \item \textbf{MSc} in Computer Science and Engineering, Eindhoven University of University,
  Eindhoven, The Netherlands, 2012. Graduated with distinction (cum laude).

  \textit{Thesis}: GText: A Language Workbench based on GLL and Term Rewriting.

  \item \textbf{BSc} in Software Engineering, Amirkabir University of Technology, Tehran, Iran, 2009.
\end{itemize}


\section*{Work Experience}

\begin{itemize}
\item \textbf{Researcher}, CWI, Amsterdam, The Netherlands. \textbf{December 20012--present}.
\item \textbf{Software Developer}, ITOrbit, Tehran, Iran. \textbf{March 2009--July 2010}.
\end{itemize}

\section*{Technical Skills} 

\begin{itemize}
\item Expert in Java, proficient in Scala, and familiar with C, Swift, Ruby, and Python
\end{itemize}


\nocite{*}
\bibliographystyle{unsrt}

\renewcommand\refname{Publications}
\bibliography{publications.bib}


\section*{Talks}

\begin{itemize}
\item A Practical Data-Dependent Parsing Framework. At PEPM'16 (paper presentation),
19 January 2016, St. Petersburg, FL, USA.

\item Meerkat Parsers: A general parser combinator library for real programming languages.
At ScalaDays 2015 Amsterdam (with Anastasia Izmaylova), 9 June 2015, Amsterdam,
The Netherlands.

\item Faster, Practical GLL Parsing. At CC'15 (paper presentation), 18 April 2015,
London, UK.

\item Safe Specification of Operator Precedence Rules. At SLE'13 (paper presentation),
26 October 2013, Indianapolis, IN, USA.

\item Iguana: an Object-Oriented Lazy Scannerless Parser. At Parsing@SLE'13. 
26 October 2013, Indianapolis, IN, USA.

\end{itemize}

\section*{Languages}

\begin{minipage}{.5\textwidth}
\begin{itemize}
\item Persian: native language
\item English: Fluent
\end{itemize}
\end{minipage}
\begin{minipage}{.5\textwidth}
\begin{itemize}
\item Dutch: Intermediate (level B2)
\item German: Intermediate (level B2)
\end{itemize}
\end{minipage}

\bigskip

\begin{center}
  \begin{footnotesize}
    Last updated: \today
  \end{footnotesize}
\end{center}

\end{document}
